TODOs

### 2015-03-19 Rmarkdown/TODO.Rmd
Updated TODOs

- [ ] Find a `wordcount` function for LaTeX or markdown files.

>>>>

- [x] Find a `wordcount` function for LaTeX or markdown files.
  - Use `texcount` ([http://stackoverflow.com/questions/2974954/correct-word-count-of-a-latex-document](http://stackoverflow.com/questions/2974954/correct-word-count-of-a-latex-document)).
